The Error Estimate of Force Calculation in the Inhomogeneous Molecular Systems

### 2012-02-27 shortRange.inhomo/alltext/pubilsh/letter.to.referee/letter-jctc.tex
add missing files

\begin{letter}{
    The Referees of\\
    Physical Chemistry Chemical Physics\\
    \vskip 1cm
  }
% \begin{picture}(0,0)
%   \put(-30,22){
%     \parbox{0.25\textwidth}{
% %	\includegraphics[scale=0.4]{logo-icp-notext.pdf}
%     }
%   }
%   \put(264,10){
%     \parbox{0.25\textwidth}{
% 	\includegraphics[scale=0.28]{Fub-logo.eps}
%     }
%   }
% \end{picture}

\opening{Dear Referees,\vskip .5cm}
Hereby we would like to submit our article:\\

@@

\textbf{Physical Chemistry Chemical Physics}, as a regular article.\\

>>>>

\begin{letter}{
    The Editors of\\
    Journal of Chemical Theory and Computation\\
    \vskip 1cm
  }
% \begin{picture}(0,0)
%   \put(-30,22){
%     \parbox{0.25\textwidth}{
% %	\includegraphics[scale=0.4]{logo-icp-notext.pdf}
%     }
%   }
%   \put(264,10){
%     \parbox{0.25\textwidth}{
% 	\includegraphics[scale=0.28]{Fub-logo.eps}
%     }
%   }
% \end{picture}

\opening{Dear Editors,\vskip .5cm}
Hereby we would like to submit our article:\\

@@

\textbf{Journal of Chemical Theory and Computation}, as a regular article.\\
